\LARGE \bf Attack Graph Generation for Micro-service Architecture

### 2018-08-10 paper_own_docker/main.tex
Sections related work and evaluation are done. Minor mistakes corrected in proposed method and references added.

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
\usepackage[options]{algorithm2e}                                     % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper
\usepackage{graphicx}
\graphicspath{ {./images/} }
\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

@@

@@

Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the internet. There the attacker performs multiple steps to achieve his goal, i.e. gaining privileges of the goal container. Some works use model checkers with goal property(Sheyner reference). They However model checkers as a disadvantage have a state explosion.(Ingols reference)

Others use breath first search algorithm. (Ingols reference)  They model the

Others have extended this work by generating attack graphs with using rule pre- and postcondtions in generating attacks.(reference) They define a specific test of rules and test their correctness.

Containers, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference). To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
 They dont use Clair as well. They do not offer any performance comparison between different topologies.

@@

In Docker, distinction is being made between the terms image, container and service. Image is an executable package that includes everything needed to run an application,  container is a runtime instance of an image and service represents a container in production. A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on. In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.

In this work we model an attack graph as a sequence of atomic attacks. Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege. A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container. For example, let us suppose that an attacker wants to have access to a database of a certain website. In order to reach the database, he has to pass other containers between him and the database. He does that by finding a vulnerability to exploit and give access to the container's neighbors. After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions. Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security. For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.

@@

Atomic attacks are fundamental building blocks in our attack graph. A single atomic attack represents a successful vulnerability exploitation. A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph. For an atomic attack to be executed, two constraints are imposed. First, the containers have to be connected between each other, so that physical access can be ensured. Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level. We model the privileges into a hierarchy. The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised. Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.

Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met. Preconditions are privilege levels that are required so that a vulnerability can be exploited. When an atomic attack is successfully executed, a postcondition is obtained. Postconditions are privileges acquired as a result of a successful attack. Both the Pre- and Postconditions are transformed from pre- and postcondition rules. We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.

@@

In order to show how the attack graph generation works in practice, we present a small example. The example is taken from the Netflix OSS Github repository. Displayed on figure \ref{TopologyGraph} is the topology of the example. The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes. On figure \ref{AttackGraph}, we can see a part of the resulting attack graph. An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege. Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege. Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege. It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka. Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.

@@

\subsubsection{Technical Details}
Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair and Clairctl for vulnerabilities generation.

@@

\subsubsection{Topology Parser}
The topology of Docker containers can be described at either runtime, or statically by using Docker Compose. In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning. Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system. However different version of docker-compose.yml, use different syntax. For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers. In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.

@@

	\caption{Table with graph characteristics(no. of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process). The examples are composed of two containers: Phpmailer and Samba. The Phpmailer container has 181, while the Samba container has 367 vulnerabilities. The topology time is the time required to generate the graph topology. The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions. The Breath-First Search is the main component that generates the attack graph. All of the components are executed five times for each of the examples and their final time is averaged. The times are given in seconds. The total time contains the topology parsing, the attack graph generation and some minor processes. However, the total time does not include the vulnerability analysis by Clair. Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}

@@

\subsubsection{Vulnerability Parser}
In the preprocessing step, we use Clair to generate the vulnerabilities of a given container. Clair is a tool that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability. Attack vector is an entity that describes which conditions and effects are connected to this vulnerability. The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete). Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image. As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.

@@

We here first preprocess the vulnerabilities and convert them into sets of pre- and postconditions. In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules. When a subset of attack vector fields and description keywords match a given rule, we use the pre- or postcondition of that rule. If more than one rule match, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions. If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition.This results in a list of container vulnerabilities with their preconditions and postconditions.

@@

After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted. Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
Breadth-first search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph. Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.

The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied. If the neighbor was not passed, then we add it to the queue. The algorithm terminates when the queue is empty. Furthermore BFS is characterized by the following properties:

@@

An attack graph system needs to be scalable because in a real world scenario, there are many containers interconnected to each other. (some references and description with statistics). In this section, we first have a look at how others evaluate their proposed systems. We will then conduct few experiments in order to test the scalability of our system with different number of containers and links between them in both synthetically-made and real networks.

Evaluation of a given system is a usually required part, when evaluating a given program. Extensive scalability study is not available. Characteristics that vary are the number of nodes, their interconnectedness and the amount of vulnerabilities per container. All of these components contribute to the execution time. Even though the notion of attack graph vary, we hope to reach a comprehensive comparison. In our case we treat every container as a computer, and treat any physical connection between two computers as a connection between two containers.

\begin{table*}[t]
	\begin{center}
		\begin{tabular}{ |c|p{30mm}|p{20mm}|c|c|p{45mm}| } 
			\hline
			Name & Description & Technology stack & No. Containers & No. vuln. & Github link \\\hline

			Netflix OSS & Combination of containers provided from Netflix. & Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & https://github.com/Oreste-Luci/netflix-oss-example \\\hline

			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & https://github.com/dockersamples/atsea-sample-shop-app \\\hline

			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & https://github.com/dockersamples/javaee-demo \\\hline

			PHPMailer and Samba & An artificial example created from two separate containers. We use an augmented version for the scalability tests. & PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & https://github.com/opsxcq/exploit-CVE-2016-10033
			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline

@@

\end{table*}[t]

For each example describe their setup and their results.

Seyner, the attack graph has 5948 nodes and 68364 edges. The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes. They claim that the performance bottleneck is inside the graph generation procedure.(reference) Therefore model checkers are not the most suitable graph representation.

Ingols tested on a network of 250 hosts. He also tested on a simulated network of 50000 hosts in under 4 minutes. (reference) However he does this evaluation on the Multiple Prerequisite graph, which is different from ours.

Amman does not provide with scalability methods.

Evaluation pre/postconditions where achieved, but they provide no evaluation for attack graph generation.

In our scalability experiments we use Samba(reference) and Phpmailer(reference) containers which were taken from their respective Github repositories. We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system. The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.

On Table \ref{table_scalability} we can see the results of our experiments. In each of the experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing. This increase is done in a clique fashion, a node of each additional container is connected to every existing container. In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e. the docker daemon where the containers are present). Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers. The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2. For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).

Throughout the experiments, for the less connected ones, the biggest time bottleneck is the preprocessing step. However these steps are with the number of containers because the container files are analyzed only once. The attack graph generation less time than the preprocessing step. Starting from example\_500, we can notice sharp increase in the number of the BDF time to 165 seconds. For the previous example with example\_100, needed 6.5 seconds.

We also performed tests on some real examples as described on table. These examples are different from the synthetic ones presented above, since they contain less containers. Also they are in a more linear fashion. For example, in order for an attacker to reach the database, he needs to gain suitable privilege levels of multiple intermediate containers.

 We tested our generator on few other randomly selected examples from Github: NetflixOSS, Atsea Sample Shop App, and JavaEE demo. These systems are composed of different kind of technologies, different number of containers and vulnerabilities. Short summary of them is given on the table \ref{table_technologies}. We want to show that we can generalize our approach for different types of technologies.

Characteristics of the Attack Graph Generator.
 - stopping criteria (When all edges are traversed)
 - BFS is guaranteed to traverse all of the edges 
 - monothonicity no edge is visited more than once.
 - all of the vulnerabilities per edge are checked
 - only the ones that fulfill a certain precondition are added. If precondition is not fulfilled, then the edge is not added.

@@

\bibitem{c1} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.

\bibitem{c2}  CoreOS Clair. https://github.com/coreos/clair

\bibitem{c3}  Clairctl. https://github.com/jgsqware/clairctl

\bibitem{c4}  Computer Security Division of National Institute of Standards and Technology.
National vulnerability database version 2.2 (2010),
http://nvd.nist.gov/

\bibitem{c5}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski. "Practical attack graph generation for network defense." Computer Security Applications Conference, 2006. ACSAC'06. 22nd Annual. IEEE, 2006.

\bibitem{c6}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.

\bibitem{c7}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.

\bibitem{c8}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.
\end{thebibliography}

>>>>

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
\usepackage[]{algorithm2e}                                     % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper
\usepackage{graphicx}
\graphicspath{ {./images/} }
\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

@@

 Statistics. They do not offer any performance comparison between different topologies.

@@

Previous work has dealt with attack graph generation, mainly in computer networks, where multiple machines are connected to each other and the Internet. In these networks an attacker performs multiple steps to achieve his goal, i.e. gaining privileges of a specific host. Attack graphs help in analyzing this behavior. Although attack graphs are useful, constructing them manually can be a cumbersome and time-consuming process. Tools that generate vulnerabilities of specific host are available. However previous works have state that these tools alone are not enough to analyze the vulnerability of an entire network and that these tools in addition to network topology could solve this issue. Therefore, some teams have working in constructing systems that generate attack graphs automatically by using different approaches.

One of the earlier works in attack graph generation was done by Sheyner with using model checkers with goal property.\cite{ingols} Model checkers use computational logic to check if a model is correct, and otherwise, they provide a counter example. A collection of these counter examples form an attack graph. They state that model checkers satisfy a monotonicity property in order to ensure termination. However model checkers have a computational disadvantage. In the example provided, NuSMV takes 2 hours to construct the attack graph with 5948 nodes and 68364 edges(Ingols reference) As a result of this, more scalable approach was needed. Amman et al. extends this work with some simplifications and more efficient storage.\cite{amman}

Ou et al. use logical attack graph\cite{ou} and Ingols\cite{ingols} et al. use breath first search algorithm in order to tackle the scalability issue. Ingols discusses the redundancy Full and Predictive graphs and model an attack graph as a MP graph with contentless edges and 3 types of nodes. They use breath first search technique for generating the attack graph. This approach provides faster results in comparison to using model checkers. An MP graph of 8901 nodes and 23315 edges is constructed in 0.5 seconds.

Aksu et al. builds on top of Ingols's system and evaluate a set of rule pre- and postcondtions in generating attacks.\cite{aksu} They define a specific test of pre- and postcondition rules and test their correctness. In their evaluation, they use machine learning approach.

Containers and microservice architectures, despite their ever-growing popularity, have shown somewhat bigger security risks, mostly because of their bigger need of connectivity and lesser degree of encapsulation(Reference).To the best of our knowledge, there is no work that has been done so far in the area of attack graph generation for docker containers. Therefore we extend the work from Ingols\cite{ingols} and Aksu\cite{aksu} in conjuction to Clair OS to generate attack graphs for microservice architectures. Similar to computer networks, microservice architectures have a container topology and tools for analysis of containers. Containers in our model correspond to hosts, and a connection between hosts translates to a communication between containers.

@@

@@

In Docker, distinction is being made between the terms image, container and service. Image is an executable package that includes everything needed to run an application, container is a runtime instance of an image and service represents a container in production. A service only runs one image, but it codifies the way that image runs—what ports it should use, how many replicas of the container should run so the service has the capacity it needs, and so on. In our work we treat these terms equally, since we are doing a static and not runtime attack graph analysis.\cite{docker}

In this work we model an attack graph as a sequence of atomic attacks. Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege. A goal of an attacker would be to perform multiple atomic attacks to reach the desired goal container. For example, let us suppose that an attacker wants to have access to a database of a certain website. In order to reach the database, he has to pass other containers between him and the database. He does that by finding a vulnerability to exploit and gives access to the container's neighbors. After a successful exploitation of multiple intermediate containers, he finally has access to the database and its content. Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security. For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.

Atomic attacks are fundamental building blocks in our attack graph. A single atomic attack represents a successful vulnerability exploitation. A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph. For an atomic attack to be executed, two constraints are imposed. First, the containers have to be connected between each other, so that physical access can be ensured. Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level. We model the privileges into a hierarchy. The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised. Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.\cite{aksu}

Furthermore, in order for atomic attacks to be performed, certain preconditions have to be ensured. Preconditions are privilege levels that are required so that a vulnerability can be exploited. When an atomic attack is successfully executed, a postcondition is obtained. Postconditions are privileges acquired as a result of a successful attack. Both the Pre- and Postconditions are transformed from pre- and postcondition rules. We use in our attack graph generator the pre- and postconditions manually selected by experts and evaluated.\cite{aksu}

@@

In order to show how the attack graph generation works in practice, we present a small example. The example is taken from the Netflix OSS Github repository.\cite{netflixoss} Displayed on figure \ref{TopologyGraph} is the topology of the example. The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes. On figure \ref{AttackGraph}, we can see a part of the resulting attack graph. An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege. Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege. Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege. It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka. Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.

@@

\subsubsection{Technical Details}
Our system is developed for Docker 17.12.1-ce and Docker Compose 1.19.0. The code is written in Python 3.6, and we use Clair\cite{clair} and Clairctl\cite{clairctl} for vulnerabilities generation.

@@

\subsubsection{Topology Parser}
The topology of Docker containers can be described at either runtime, or statically by using Docker Compose. In our case, since we are doing static attack graph analysis, we use Docker Compose as our main tool in the beginning. Docker Compose provides us with a docker-compose.yml file which is used for extraction of the topology of the system. However different versions of docker-compose.yml, use different syntax. For example older versions use the deprecated keyword "link", while newer ones use exclusively "networks", to denote a connection between two containers. In this work, we use the keyword "networks" as an indicator that a connection between two containers exists.

@@

	\caption{Table with graph characteristics(no. of containers, nodes and edges in both the topology and attack graph) and executing times of the main attack graph generator components: Topology Parser, Vulnerability Preprocessing Module and Breadth-first Search Module(the latter two parts of the main attack graph generation process). The examples are composed of two containers: Phpmailer and Samba. The Phpmailer container has 181, while the Samba container has 367 vulnerabilities. The topology time is the time required to generate the graph topology. The vulnerabilities preprocessing time is the time required to convert the vulnerabilities into sets of pre- and postconditions. The Breath-First Search is the main component that generates the attack graph. All of the components are executed five times for each of the examples and their final time is averaged. The times are given in seconds. The total time contains the topology parsing, the attack graph generation and some minor processes. However, the total time does not include the vulnerability analysis by Clair. Evaluation of Clair can depend on multiple factors and it is therefore not in the scope of this analysis.}

@@

\subsubsection{Vulnerability Parser}
In the preprocessing step, we use Clair to generate the vulnerabilities of a given container. Clair is a vulnerability scanner that inspects a docker image, and generate its vulnerabilities by providing CVE-ID, description and attack vector for each vulnerability. Attack vector is an entity that describes which conditions and effects are connected to this vulnerability. The fields in the attack vector as described by the National Vulnerability Database(NVD) are: Access Vector(Local, Adjacent Network and Network), Access Complexity(Low, Medium, High), Authentication(None, Single, Multiple), Confidentiality Impact(None, Partial, Complete), Integrity Impact(None, Partial, Complete) and Availability Impact(None Partial Complete). Although it is very useful, Clair does not provide with an easy to use interface to analyze a docker image. As a result, we use Clairctl(Clair wrapper) in order to analyze a complete docker image.

@@

Here, we first preprocess the vulnerabilities and convert them into sets of pre- and postconditions. In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules. When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule. If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions. If no rule matches we take None as a precondition and ADMIN(OS) as a postcondition. This results in a list of container vulnerabilities with their preconditions and postconditions.

@@

After the preprocessing step is done, the vulnerabilities are parsed and their pre- and postconditions are extracted. Together with the topology, they are feed into the Breadth-First Search algorithm(BFS).
Breadth-First Search is a popular search algorithm that traverses a graph by looking first at the neighbors of a given node, before going deeper in the graph. Pseudocode of our modified Breath First Search is given in Algorithm \ref{BFSalgorithm}.

The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of nodes and edges that make the attack graph. 
The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
Then into a while loop it iterates through every node, checks its neighbors and adds the edges if the conditions are satisfied. If the neighbor was not passed, then it is added to the queue. The algorithm terminates when the queue is empty. Furthermore BFS is characterized by the following properties:

@@

In real-world microservice architectures, many containers are interconnected to each other. This raises the need for a scalable attack graph system. In this section, we first have a look at how others evaluate their systems. We then conduct few experiments in order to test the scalability of our system with different number of containers, and connections in both artificial and real networks. All of the experiments were performed on a Intel(R) Core(TM) i5-7200U CPU @ 2.50GHz with 8GB of RAM running Ubuntu 16.04.3 LTS.

Extensive scalability study of attack graph generators  is rare in current literature and many parameters contribute to the complexity of a comprehensive analysis. Characteristics that usually vary in this sort of evaluation are the number of nodes, their interconnectedness and the amount of vulnerabilities per container. All of these components contribute to the execution time of a given algorithm. Even though the definitions of an attack graph vary, we hope to reach a comprehensive comparison with current methods. In our case we compare our system to existing work by treating every container as a computer, and any physical connection between two computers as a connection between two containers.

\begin{table*}
	\begin{center}
		\begin{tabular}{ |p{20mm}|p{25mm}|p{20mm}|p{10mm}|c|p{15mm}|p{45mm}| } 
			\hline
			Name & Description & Technology stack & No. Containers & No. vuln. & Attack Graph generation time & Github link \\\hline

			Netflix OSS & Combination of containers provided from Netflix. & Spring Cloud, Netflix Ribbon, Spring Cloud Netflix, Netflix's Eureka & 10 & 4111 & 0.5120 sec. & https://github.com/Oreste-Luci/netflix-oss-example \\\hline

			Atsea Sample Shop App & An example online store application. & Spring Boot, React, NGINX, PostgreSQL & 4 & 120 & 0.2761 sec. & https://github.com/dockersamples/atsea-sample-shop-app \\\hline

			JavaEE demo & An application for browsing movies along with other related functions. & Java EE application, React, Tomcat EE & 2 & 149 & 0.2613 sec. & https://github.com/dockersamples/javaee-demo \\\hline

			PHPMailer and Samba & An artificial example created from two separate containers. We use an augmented version for the scalability tests. & PHPMailer(email creation and transfer class for PHP), Samba(SMB/CIFS networking protocol) & 2 & 548 & 0.2570 sec. & https://github.com/opsxcq/exploit-CVE-2016-10033
			https://github.com/opsxcq/exploit-CVE-2017-7494 \\\hline

@@

\end{table*}

Seyner in his work tests the system in both a small and extended examples.\cite{sheyner} The attack graph in the larger example has 5948 nodes and 68364 edges. The time needed for NuSMV to execute this configuration is 2 hours, but the model checking part took 4 minutes. Sheyner claims that the performance bottleneck is inside the graph generation procedure.

Ingols tested his system on a network of 250 hosts. He afterwards continued his study on a simulated network of 50000 hosts in under 4 minutes.\cite{ingols} Although this method yields better performance than the aforementioned approach, this evaluation is based on the Multiple Prerequisite graph, which is different from ours. In addition to this, missing explanation of how the hosts are connected, does not make it directly comparable to our method.

Ou provides some more extended study where he tests his system on more examples.\cite{ou}  He mentions that the asymptotic CPU time is between $O(n^2)$ and $O(n^3)$, where n is the number of hosts. The performance of the system for 1000 fully connected nodes takes more than 1000 seconds. He also provides an evaluation where he MulVAL clearly outperforms the Sheyner's system.

In our scalability experiments we use Samba\cite{samba} and Phpmailer\cite{phpmailer} containers which were taken from their respective Github repositories. We then extended this example and artificially made cliques of 5, 20, 50, 100, 500 and 1000 Samba containers to test the scalability of the system. The Phpmailer container has 181 vulnerabilities, while the Samba container has 367 vulnerabilities detected by Clair.

On Table \ref{table_scalability} we can see the results of our experiments. In each of these experiments the number of Phpmailer containers stays constant, while the number of Samba containers is increasing. This increase is done in a fully connected fashion, a node of each additional container is connected to every existing container. In addition, there are also two additional artificial containers("outside" that represents the environment from where the attacker can attack and the "docker host", i.e. the docker daemon where the containers are present). Therefore the number of nodes in the topology graph is the sum of: "outside", "docker host", number of Phpmailer containers and number of Samba containers. The number of edges of the topology graph is a a combination of: 1 edge("outside"-"Phpmailer"), n edges("docker host" to all of the containers) and clique of the Phpmailer and samba containers n*(n+1)/2. For example\_5, the number of containers would be 8(1 Phpmailer, 1 outside, 1 docker host and 5 Samba containers) the number of edges in the topology graph would be 32: 1 outside edge, 6 docker host edges(n=6, 1 Phpmailer and 5 Sambas) and 25 clique edges(5*6/2=15).

Throughout the experiments, for the smaller configurations, the biggest time bottleneck is the preprocessing step. However this step increases in linear fashion because the container files are analyzed only once by Clair. The attack graph generation for the smaller examples is considerably less than the preprocessing time. Starting from example\_500, we can notice sharp increase in BDF execution time to 165 seconds. For the previous example with example\_100, needed attack graph generation time is 6.5 seconds.

We also performed tests on some real examples as described on table \ref{table_technologies} and extend our system to different types of technologies, number of containers and vulnerabilities. The examples are as follows: NetflixOSS, Atsea Sample Shop App, and JavaEE demo. These examples are different from the synthetic ones presented above, since they contain less and different containers. They are connected in a more linear fashion in contrast to the full connection provided in the previous example. For example, in order for an attacker to reach a database, he needs to gain suitable privilege levels of multiple intermediate containers in several steps.

@@

\bibitem{docker} Merkel, Dirk. "Docker: lightweight linux containers for consistent development and deployment." Linux Journal 2014.239 (2014): 2.

\bibitem{clair}  CoreOS Clair. https://github.com/coreos/clair

\bibitem{clairctl}  Clairctl. https://github.com/jgsqware/clairctl

\bibitem{nvd}  Computer Security Division of National Institute of Standards and Technology.
National vulnerability database version 2.2 (2010),
http://nvd.nist.gov/

\bibitem{ingols}  Ingols, Kyle, Richard Lippmann, and Keith Piwowarski. "Practical attack graph generation for network defense." Computer Security Applications Conference, 2006. ACSAC'06. 22nd Annual. IEEE, 2006.

\bibitem{aksu}  Aksu, M. Ugur, et al. "Automated Generation Of Attack Graphs Using NVD." Proceedings of the Eighth ACM Conference on Data and Application Security and Privacy. ACM, 2018.

\bibitem{sheyner}  Sheyner, Oleg, et al. "Automated generation and analysis of attack graphs." Security and privacy, 2002. Proceedings. 2002 IEEE Symposium on. IEEE, 2002.

\bibitem{netspa}  Artz, Michael Lyle. Netspa: A network security planning architecture. Diss. Massachusetts Institute of Technology, 2002.

\bibitem{amman}  Ritchey, Ronald W., and Paul Ammann. "Using model checking to analyze network vulnerabilities." Security and Privacy, 2000. S\&P 2000. Proceedings. 2000 IEEE Symposium on. IEEE, 2000.

\bibitem{ou}  Ou, Xinming, Wayne F. Boyer, and Miles A. McQueen. "A scalable approach to attack graph generation." Proceedings of the 13th ACM conference on Computer and communications security. ACM, 2006.

\bibitem{samba} https://github.com/opsxcq/exploit-CVE-2017-7494

\bibitem{phpmailer} https://github.com/opsxcq/exploit-CVE-2016-10033

\bibitem{netflixoss} https://github.com/Oreste-Luci/netflix-oss-example
\end{thebibliography}
